A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
cap void
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@985 43ef1190-90fd-4dd7-a769-d0121f02b80e
Acknowledgements
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@986 43ef1190-90fd-4dd7-a769-d0121f02b80e

A change periodicity predicate should be standardized in Void.

@@

>>>>

A change periodicity predicate should be standardized in VoID.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Axel Polleres for inspiring me to start this study, to
Martin Giese for careful review and critical comments, and Gregory
Todd Williams for promptly solving issues in the underlying libraries
used in this study.
